---
title: "p8105_hw1_sl4836"
author: "Hun"
date: "9/27/2021"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE}
random_sample_from_std_norm_dist <- rnorm(10, mean = 0, sd = 1)

logical_vector <- ifelse(random_sample_from_std_norm_dist>0, TRUE, FALSE)

character_vector <- rep(c("apple", "banana", "peach"),length.out = 10)

factor_vector <- factor(rep(c("low","middle","high"), length.out = 10))
```


```{r, message=FALSE}
random_sample_from_std_norm_dist
logical_vector
character_vector
factor_vector
```

```{r, message=FALSE}
library(tidyverse)

data("penguins", package = "palmerpenguins")

name_variables <- names(penguins)

nrow <- nrow(penguins)
ncol <- ncol(penguins)

levels_species <- levels(penguins$species)
levels_sex <- levels(penguins$sex)
levels_island <- levels(penguins$island)

mean_bill_length <- penguins %>% drop_na() %>% summarise(mean(bill_length_mm)) %>% round(digits = 3)

sd_bill_length <- penguins %>% drop_na() %>% summarise(sd(bill_length_mm)) %>% round(digits = 3)

mean_bill_depth <- penguins %>% drop_na() %>% summarise(mean(bill_depth_mm)) %>% round(digits = 3)

sd_bill_depth <- penguins %>% drop_na() %>% summarise(sd(bill_depth_mm)) %>% round(digits = 3)

mean_flipper_length <- penguins %>% drop_na() %>% summarise(mean(flipper_length_mm)) %>% round(digits = 3)

sd_flipper_length <- penguins %>% drop_na() %>% summarise(sd(flipper_length_mm)) %>% round(digits = 3)

mean_body_mass <- penguins %>% drop_na() %>% summarise(mean(body_mass_g)) %>% round(digits = 3)

sd_body_mass <- penguins %>% drop_na() %>% summarise(sd(body_mass_g)) %>% round(digits = 3)
```
The size of the dataset is **`r nrow` ** x **`r ncol`.**

There are **`r ncol`** variables: *`r name_variables`.*

The levels of **speices** are **`r levels_species` **

The levels of **island** are **`r levels_island` **

The levels of **sex** are **`r levels_sex` **

The **mean** of the bill_length_mm is **`r mean_bill_length`mm.**

The **standard deviation** of the bill_length_mm is **`r sd_bill_length`.**

The **mean** of the bill_depth_mm   is **`r mean_bill_depth`mm.**

The **standard deviation** of the bill_depth_mm   is **`r sd_bill_depth`.**

The **mean** of the flipper_length_mm    is **`r mean_flipper_length`mm.**

The **standard deviation** of the flipper_length_mm  is **`r sd_flipper_length`.**

The **mean** of the body_mass_g   is **`r mean_body_mass`g.**

The **standard deviation** of the body_mass_g   is **`r sd_body_mass`.**


```{r}
scatter_plot <- penguins %>% drop_na() %>% ggplot() + geom_point(aes(bill_length_mm, flipper_length_mm, color = species))

ggsave("scatterplot_hw1.pdf", plot = scatter_plot) 
```


